%-------------------------
% Resume in Latex
% Author: Harshibar
% Based off of: https://github.com/jakeryang/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tikz}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=dark-grey,
    }
% only for pdf latex
% \input{glyphtounicode}

% font awesome
% \usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: Helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.5pt}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO SERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdf latex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default left margin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

% CTFline logo
\newcommand{\myCtftime}{\tikz[y=1em, x=1em, baseline=1pt]{
  \path[fill, even odd rule] (0,0) -- (1.05,0) -- (1.05,1) -- (0,1) -- cycle
    (.15,.15) -- (.9,.15) -- (.9,.85) -- (.15,.85) -- cycle
    (.15,.85) -- (.35,.85) -- (.7,.5) -- (.45,.25) -- (.35,.35) -- (.5,.5) -- cycle; 
  }
}
\newcommand{\ctftime}[2]{\myCtftime}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Samrath Sudesh Acharya} \\ \vspace{5pt}
    % \small \faPhone \texttt{+919538533738} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:samrathsacharya@gmail.com}{samrathsacharya@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faLinkedinSquare \hspace{2pt} \href{https://www.linkedin.com/in/samrath-sudesh-acharya/}{Samrath Sudesh Acharya} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/samrath-sudesh-acharya}{samrath-sudesh-acharya}
    \hspace{1pt} $|$
    \newline
    \hspace{1pt} \faGlobe \hspace{2pt} \href{https://samrathsacharya.me/}{Blog Website} $|$
    \hspace{1pt} \ctftime \hspace{2pt} \href{https://ctftime.org/user/169231}{CTFtime Profile} $|$
    \hspace{1pt} \faMapMarker \hspace{2pt}\texttt{Mangalore, India} 
    \\ \vspace{-3pt}
\end{center}

%-----------EDUCATION-----------
% \section {EDUCATION}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Dayananda Sagar College of Engineering}{Dec 2020 - Present}
%       {B.E. in Computer Science Engineering}{Bangalore, India}
%       %\resumeItemListEnd
        
%     \resumeSubheading
%       {Sharada P.U. College}{Apr 2018 - Mar 2020}
%       {PCMC Stream | 92\%}{Mangalore, India}
%     %   	\resumeItemListStart
%     % 	\resumeItem {\textbf{Award}: Achieved \textbf{1st Position} in C++ coding competition among \textbf{15} college , held in \newline Pre-Unique,ST.Aloysius College, Mangalore}
%     %     \resumeItemListEnd
    
%     \resumeSubheading
%       {Indian School Al Wadi Al Kabir}{Apr 2005 - Feb 2018}
%       {C.B.S.E | 89\%}{Sultanate of Oman}
%   \resumeSubHeadingListEnd
%--------------------------------

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages} {: Python, JavaScript, HTML, CSS, SQL (MySQL), Dart, Flutter, C, C++}\vspace{2pt} \\
     \textbf{Tools}     {: GitHub, BurpSuite, Metasploit, Postman, Docker, Linux, ElasticSearch, Kibana, Flare-VM, 
     ExtraHop, InsightAppSec, Intezer Analyser}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Tracelay}{November. 2022 -- February. 2023}
      {Cyber Security Analyst Trainee}{ India}
     \resumeItemListStart
      {Wrote reports on various APT attacks using industry-level tools like Trend Micro XDR, Sophos XDR, ExtraHop NDR, Intezer Cloud, Rapid 7 App sec}
      \resumeItemListEnd
  

    \resumeSubheading
      {Embrays Technologies}{December. 2021 -- January. 2022}
      {Intern as a Flutter Developer}{ India}
     \resumeItemListStart
      {Developed a production-ready Android app with GraphQl API Integration and Firebase which has \href{https://play.google.com/store/apps/details?id=com.easemytrades.stockdaddy&hl=en_IN&gl=US}{\textbf{\myuline {1L+ downloads}}}, providing seamless user experience and leveraging the power of GraphQL and Firebase.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
      
%-----------CERTIFICATION-----------    
     
\section{CERTIFICATION}
% \resumeSubHeadingListStart
    \resumeItemListStart [itemsep=1.5pt] %if you want all the points close
    % \resumeItemListStart
        \resumeItem{\textbf{\href{https://certs.ine.com/ca238e43-604f-4f41-9e62-f29c8f79818c\#gs.4ifedx}{\myuline{Junior Penetration Tester (eJPT) | INE}}}}
        \resumeItem{\textbf{\href{https://academy.tcm-sec.com/courses/1547503/certificate}{\myuline{Practical Malware Analysis \& Triage | TCM Security}}}}
        \resumeItem{\textbf{\href{https://www.credly.com/badges/85ea6107-d938-4291-be64-8d665ede181f/linked_in_profile}{\myuline{Foundations of Operationalizing MITRE ATT\&CK | AttackIQ}}}}
    \resumeItemListEnd
% \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
              
    \resumeProjectHeading
          {\textbf{Mac-Changer
          (\href{https://github.com/samrath-sudesh-acharya/Mac-Changer}{\myuline {GitHub}})}}{Sept. 2020 -- Nov. 2020}
          \resumeItemListStart
            \resumeItem{A tool that allows for quick and easy mac-address changes on Linux machines, with over {\textbf{100+ clone on \myuline{GitHub}}}.}
            \resumeItem{Utilized \textbf{bash scripting} to create a versatile tool that is compatible with \textbf{any Linux distro}, making it a must-have tool for Linux enthusiasts and network professionals.}
          \resumeItemListEnd
          
     \resumeProjectHeading
          {\textbf{System Security Check (\href{https://github.com/samrath-sudesh-acharya/SystemSecuirtyCheck}{\myuline {GitHub}})}}{Sept. 2020 -- Nov. 2020}
          \resumeItemListStart
            \resumeItem{A robust multi-layered cybersecurity strategy, uncovering vulnerabilities and potential attack vectors by scanning for Open Port, Viruses, MIME, and Windows Firewall Rules.}
            \resumeItem{Utilized \textbf{Python} libraries \textbf{Socket} and \textbf{Pymongo} to create a feature-rich executable file that scans the system and stores in  \textbf{MongoDB} database, which can be viewed on the website.}
          \resumeItemListEnd  
          
    \resumeProjectHeading
          {\textbf{Pragati (\href{https://github.com/samrath-sudesh-acharya/Education-Chatbot-}{\myuline {GitHub}})}}{Sept. 2020 -- Nov. 2020}
          \resumeItemListStart
            \resumeItem{A WhatsApp Chatbot to transform career guidance via an intelligent, personalized path to education and dream jobs with the help of a robust machine learning algorithm.}
            \resumeItem{Leveraged \textbf{Python} libraries \textbf{Selenium}, \textbf{Matplotlib}, \textbf{Keras}, \textbf{NLTK} to understand user input for web scraping and providing data visualization with the help of \textbf{MongoDB} database and \textbf{FastAPI} RESTAPI deployed in \textbf{AWS}.}
          \resumeItemListEnd  
          
          
    \resumeSubHeadingListEnd

\section{ACHIEVEMENTS}
    % \resumeSubHeadingListStart
        \resumeItemListStart [noitemsep] %if you want all the points close
        % \resumeItemListStart
            \resumeItem{Smart India Hackathon Finalist 2023 among 500 teams in India }
            \resumeItem{Ranked \textbf{181} globally among 4284 teams in Huntress CTF}
            \resumeItem{Ranked \textbf{2} globally in WU CTF and EnigmaXplore CTF, InfoFest CTF, DeconstruCT.F 23}
            \resumeItem{Ranked \textbf{24} out of 550 teams in TechGig Airtel Hackathon, EdTech category}
            \resumeItem{Ranked \textbf{top 10} winner across India in Citi Bank Innovation Hackathon 2022}
        \resumeItemListEnd
    % \resumeSubHeadingListEnd

\begin{comment}
    \resumeSubheading
      {Google Verily}{Aug. 2018 -- Sept. 2019}
      {Software Engineer}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{\textbf{Led front-end development} of a dashboard to process 50k blood samples and detect early-stage cancer}
        \resumeItem{Rebuilt a Quality Control product with input from 20 cross-functional stakeholders, \textbf{saving \$1M annually}}
        \resumeItem{Spearheaded product development of a new lab workflow tool, leading to a 40\% increase in efficiency; \\ shadowed 10 core users, iterated on design docs, and implemented the solution with one engineer}

    \resumeItemListEnd

    \resumeSubheading
      {Amazon}{May 2017 -- Aug. 2017}
      {Software Engineering Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Worked on the Search Customer Experience Team; \textbf{received a return offer} for a full-time position}
        \resumeItem{\textbf{Shipped a new feature to 2M+ users} to improve the search experience for movie series-related queries}
        \resumeItem{Built a back-end database service in Java and implemented a front-end UI to support future changes}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\end{comment}

%-------------------------------------------
\end{document}
